ms2

### 2017-05-03 ms2/ms2.Rmd
updating

@@

all_ineq = read_tsv('data/all_drug_ineq.tsv') %>%
  left_join(regions, by='state')
state_ineq = read_tsv('data/drug_ineq.tsv')
hrr_ineq = read_tsv('data/hrr_drug_ineq.tsv')
```

@@

```{r load_abg}
resistance_groups = read_tsv('resistance_groups.tsv')

organisms = c('Escherichia coli',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Enterococcus faecium',
              'Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')

abg = read_tsv('../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by=c('zipcode', 'state')) %>%
  right_join(resistance_groups, by='drug') %>%
  filter(bug %in% organisms) %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

possible_bug_drug = read_tsv('bug_drug2.tsv')

@@

abg %<>% right_join(good_combos, by=c('bug', 'drug_group'))

@@

```{r ecoli_quin, cache=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Escherichia coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()

left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Escherichia coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='black', se=FALSE) +
  geom_point() +
  geom_text() +
  xlim(0.2, 0.45) + ylim(0, 50) +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```

@@

```{r}
left_join(hrr_abg, hrr_ineq, by=c('hrr', 'drug_group')) %>%
  left_join(hrr, by='hrr') %>%
  filter(bug=='Escherichia coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region, size=sqrt(total))) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```

@@

```{r ecoli_bactrim}
ecoli_bactrim_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='Escherichia coli', drug_group=='tmp_smx') %>%
  filter(!is.na(mean_percent_nonsusceptible))

@@

>>>>

**swo**: filter the NAs in the abg earlier

@@

all_ineq = read_tsv('data/state_ineq_all_2011.tsv') %>%
  left_join(regions, by='state')
state_ineq = read_tsv('data/state_ineq_2011.tsv')
hrr_ineq = read_tsv('data/hrr_ineq_2011.tsv')
```

@@

```{r load_abg}
resistance_groups = read_tsv('resistance_groups.tsv')
bug_names = read_tsv('bug_names.tsv')

abg = read_tsv('../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by=c('zipcode', 'state')) %>%
  right_join(resistance_groups, by='drug') %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

possible_bug_drug = read_tsv('bug_drug.tsv')

@@

abg %<>% right_join(good_combos, by=c('bug', 'drug_group')) %>%
  rename(bug_long=bug) %>% left_join(bug_names, by='bug_long') %>% select(-bug_long)

# check that all the short names made it in
if (any(is.na(abg$bug))) stop('missing bug names')

@@

```{r ecoli_quin, cache=FALSE}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region)) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()

left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='black', se=FALSE) +
  geom_point() +
  geom_text() +
  xlim(0.2, 0.45) + ylim(0, 50) +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```

@@

```{r}
left_join(hrr_abg, hrr_ineq, by=c('hrr', 'drug_group')) %>%
  left_join(hrr, by='hrr') %>%
  filter(bug=='E. coli', drug_group=='quinolone') %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=region, size=sqrt(total))) +
  geom_smooth(aes(x=mean, y=mean_percent_nonsusceptible, color=NULL), method='lm', col='black') +
  geom_point() +
  xlab('quinolone claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```

@@

```{r ecoli_bactrim}
ecoli_bactrim_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='tmp_smx') %>%
  filter(!is.na(mean_percent_nonsusceptible))

@@

## E.coli and penicillin

```{r}
ecoli_pen_dat = left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  left_join(regions, by='state') %>%
  filter(bug=='E. coli', drug_group=='penicillin') %>%
  filter(!is.na(mean_percent_nonsusceptible))

ecoli_bactrim_dat %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  #scale_x_continuous(limits=c(0.08, 0.2), breaks=c(0.08, 0.1, 0.15, 0.2)) +
  #ylim(10, 45) +
  #xlab('TMP/SMX claims per beneficiary') + ylab('mean percent nonsusceptible E. coli isolates') +
  theme_minimal()
```
